\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-09-17 analysis/manuscript.Rmd
Minor

From a data perspective, research institutions and funders need to push towards price transparency in scholarly publishing to enable such evaluations. 
The reporting of open access funding, including transformative agreements, is also not harmonised, but often crowd-sourced from various sources.
To improve the assessment of transformative agreements, libraries and publishers should collaborate on standards and services to publicly share information about respective journal portfolios, participating institutions and open access invoicing, for example in the international context of ESAC and the Barcelona Declaration on Open Research Information.
Such collaboration would help overcome the limitations of current approaches that derive funding for open access from authorship data.

>>>>

From a data perspective, research institutions and funders need to push towards price transparency in scholarly publishing to enable these evaluations. 
The reporting of open access funding, including transformative agreements, is also not harmonised, but often crowd-sourced from various sources.
To improve the assessment of transformative agreements, libraries and publishers should collaborate on standards and services to publicly share information about respective journal portfolios, participating institutions and open access invoicing, for example in the international context of ESAC and the Barcelona Declaration on Open Research Information.
Such collaboration would help overcome the limitations of current approaches that derive funding for open access from authorship data.
